---
title: "Contributing articles"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

If you are a student at the Hertie School who is interested in sharing your project, please follow the instructions below to contribute an article to this blog. 

### General Instructions {#instructions}

Articles posted on the Data Science Student Projects website are authored using [Distill for R
Markdown](https://rstudio.github.io/distill). The steps required to
contribute a new article are as follows:

1. Fork the [Distill template repository](https://github.com/hertie-data-science-lab/distill-template) to host your article. We will use this repository for feedback and review before publishing your article. 

2. Replace the [article metadata](#article-metadata) fields in the template with information about your article. 

3. If your article is based off of a report originally written in LaTeX, [convert your TeX file to Markdown format](#file-conversion) and copy/paste text from the body of the converted Markdown file into your article template. {#after-conversion}

4. Make in-line edits as needed to meet our [general formatting](#formatting-guidelines) guidelines, and knit your `.Rmd` file. Commit and push the final version of the article to your Github repository. 

5. [Post an issue](https://github.com/hertie-data-science-lab/student-projects) on the Data Science Student Projects GitHub repo to submit a request for publishing your article. Please include a link back to your article's GitHub repo. Once we see your issue, we'll take a look at your article, suggest changes as necessary, then publish it when it's ready.

### Article metadata {#article-metadata}

Your article should include some standard metadata fields. Here's an example of a heading that includes all required metadata:

``` {.markup}
---
title: "Some Interesting Title Here"
description: |
  Using some fancy deep learning method to do something vaguely interesting 
  that is at least tangentially related to politics/computational social science. 
author:
  - name: Allison Koh 
  - name: Author 2
date: 07-17-2020
categories: 
  - Natural Language Processing
  - Machine Learning
bibliography: bibliography.bib
creative_commons: CC BY
repository_url: https://github.com/allisonkoh/project-repo
output: 
  distill::distill_article:
    self_contained: false
preview: figures/BERTfig3.png
---
```

Please note the following: 

1. You can include multiple authors in the `author` field, and the field includes an option to include URLs if you would like to add a link to your personal website. 

2. In the `categories` field, list the course(s) you took as a part of your project submission. Courses offered by the data science lab include: *Machine Learning*, *Natural Language Processing*, and *Python Programming for Data Scientists*.

3. The `creative_commons` field marks the article as being 
share-able (all contributed posts must have a [Creative Commons](https://creativecommons.org/) license). 

4. The `repository_url` is used to provide links from the article back to GitHub.

5. Select a `preview` figure that best represents your findings. 

### Converting TeX files to Markdown {#file-conversion}

If your article is based off of a report originally written in LaTeX, you can use `pandoc` to convert your article to the Markdown (`*.md`) format required  We recommend using the `{rmarkdown}` package in `R` for file conversion. 

Before file conversion, make sure you have the following documents in the same repository: 

- LaTeX (`*.tex`) file 
- Bibliography (`*.bib`) file
- Figures folder (**NOTE: Make sure figures are saved as `*.png` files.**)
- Any other cross-referenced materials  

After compiling your article repo and ensuring you have the latest versions of `{rmarkdown}` and `{knitr}`, use the `rmarkdown::pandoc_convert()` function to convert your TeX file to Markdown (`*.md`) format. The code you run should look something like this: 

```{r convert-tex-md, echo = TRUE, eval = FALSE}
rmarkdown::pandoc_convert(
  "bertcnn-classifying-manifestos.tex", 
  to = "markdown", 
  output = "bertcnn-classifying-manifestos.md", 
  citeproc = TRUE
)
```

Once your `*.md` file has compiled, continue on from Step 3 in the [instructions](#instructions) above. 
<!-- Guidelines for installing and using `pandoc` for file conversion can be found here: https://pandoc.org/getting-started.html -->

### Formatting Guidelines and Recommendations {#formatting-guidelines}

You can use the following list of guidelines for your article to meet general formatting requirements. Please note that in-line edits necessary to publish the final version of an article will vary on a case-by-case basis.

- All section headings start with __`##`__, and all sub-headings start with __`###`__.
- Citations are formatted correctly^[You might run into issues with bibliography files imported from some citation management programs (i.e. Mendeley).].
- Figures are high-quality in resolution. 
- Cross references to figures, tables, and sections are formatted correctly.
- (Most importantly) The `.Rmd` file knits with no issues. 

In addition to these general guidelines, we also recommend converting tables into figures (full color) when possible.

### Questions? 

Please feel free to reach out at any point in the process of contributing your article for advice and feedback. You can direct questions about submitting your work to [Allison Koh](mailto:koh@hertie-school.org). 
